The YUIMA Project: a Computational Framework for Simulation and Inference of Stochastic Differential Equations

### 2013-03-09 pkg/yuimadocs/inst/doc/JSS/article-new.Rnw
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@235 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Miscellanea and Roadmap of YUIMA Project}\label{sec6}
Other statistical techniques are already implemented or will be shortly released in the \pkg{yuima}. For example, a nice utility is the function \code{toLatex} for objects of class \code{yuima} and \code{yuima.model}. A simple writing like
\code{toLatex(my-yuima-obj)} produces the related \LaTeX{} code which can be copy and pasted in a mathematical paper.
We also plan to open the the contribution to the YUIMA project to external developers in the near future.

>>>>

\section{Miscellanea and Roadmap of YUIMA Project}\label{sec6}
Other statistical techniques are already implemented in the developer version of the \pkg{yuima} package. Among these: the QMLE approach for stochastic differential equations with L\'evy component, the estimation for the fractional Ornstein-Uhlembeck model \citep{brouiac12},

or will be shortly released in the \pkg{yuima}. For example, a nice utility is the function \code{toLatex} for objects of class \code{yuima} and \code{yuima.model}. A simple writing like
\code{toLatex(my-yuima-obj)} produces the related \LaTeX{} code which can be copy and pasted in a mathematical paper.
We also plan to open the the contribution to the YUIMA project to external developers in the near future.
